target_offtarget

### 2025-01-22 manuscript_figures.Rmd
Figure S3 update

library(tidyverse)
library(ggpubr)
library(tidyplots)
library(ggthemes)

@@

total_reads <- 
  reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(total_reads),
    colour = Background
  )) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_x_log10(labels = scales::label_log10()) + xlab("Viral load (copies / ml)") +
  ggtitle("Total Reads") +
  ylab("log10(Total Reads)") +
  scale_color_manual(values = cols2, labels = c("P1", "P2"))

viral_reads <- 
  reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(viral_reads),
    colour = Background
  )) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_x_log10(labels = scales::label_log10()) + xlab("Viral load (copies / ml)") +
  ggtitle("Total Viral Reads") +
  ylab("log10(Total Viral Reads)") +
  scale_color_manual(values = cols2, labels = c("P1", "P2"))

ATCC_reads <- 
  reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(ATCC_reads),
    colour = Background
  )) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_x_log10(labels = scales::label_log10()) + xlab("Viral load (copies / ml)") +
  ggtitle("Spike In Viral Reads") +
  ylab("log10(Spike In Viral Reads)") +
  scale_color_manual(values = cols2, labels = c("P1", "P2"))

prop_ATCC <- reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(x = Viral.load, y = prop_ATCC, colour = Background)) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_x_log10(labels = scales::label_log10()) + xlab("Viral load (copies / ml)") +
  ggtitle("Proportion Spike In Viral") +
  ylab("Spike In Viral Reads/Total Reads") +
  scale_color_manual(values = cols2, labels = c("P1", "P2"))

prop_viral <- reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(x = Viral.load, y = prop_viral, colour = Background)) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_x_log10(labels = scales::label_log10()) + xlab("Viral load (copies / ml)") +
  ggtitle("Proportion Viral") +
  ylab("Viral Reads/Total Reads") +
  scale_color_manual(values = cols2, labels = c("P1", "P2"))

@@

### ***Final plot***
```{r}
ggarrange(total_reads,
          viral_reads,
          prop_viral,
          nrow = 3,
          common.legend = TRUE,
          align = "hv")

@@

#ggsave("figures/manuscript_figures_pdf/FigureS3.pdf")

@@

## Figure S4

>>>>

library(tidyverse)
library(ggpubr)
library(tidyplots)
library(ggthemes)
library(scales)

@@

total_reads <- 
  reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = (total_reads),
    colour = Background
  )) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_y_log10(labels = scales::trans_format("log10", scales::label_math())) + 
    scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + xlab("Viral load") +
  # ggtitle("All") +
  ylab("Total number of reads") +
  scale_color_manual(values = cols2, labels = c("P1", "P2"))

viral_reads <- 
  reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = (viral_reads),
    colour = Background
  )) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_y_log10(labels = scales::trans_format("log10", scales::label_math())) + 
    scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + xlab("Viral load") +
  # ggtitle("Viral reads") +
  ylab("Number of viral reads") +
  scale_color_manual(values = cols2, labels = c("P1", "P2"))

ATCC_reads <- 
  reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = (ATCC_reads),
    colour = Background
  )) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_y_log10(labels = scales::trans_format("log10", scales::label_math())) + 
    scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + xlab("Viral load") +
  ggtitle("Spike-in Viral Reads") +
  ylab("Spike-in Viral Reads") +
  scale_color_manual(values = cols2, labels = c("P1", "P2"))

prop_ATCC <- reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(x = Viral.load, y = prop_ATCC, colour = Background)) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
    scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + xlab("Viral load") +
  ggtitle("Spike-in viral reads") +
  ylab("Proportion") +
  scale_color_manual(values = cols2, labels = c("P1", "P2"))

prop_viral <- reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(x = Viral.load, y = prop_viral, colour = Background)) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
 scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + xlab("Viral load") +
  # ggtitle("Viral reads") +
  ylab("Proportion of viral reads") +
  scale_color_manual(values = cols2, labels = c("P1", "P2")) + scale_y_continuous(limits=c(0,1.0))

@@

### ***Final plot***
```{r, warning=FALSE, echo=FALSE, message=FALSE}

ggarrange(total_reads,
          viral_reads,
          prop_viral,
          nrow = 3,
          common.legend = TRUE,
          align = "hv")

@@

ggsave("figures/manuscript_figure_2025/PDF/Figure_S3.pdf", 
       width = 8,
       height = 8)

@@

## Not required ?Figure S4
